The value of intermediation

### 2023-04-09 src/paper/theory.tex
Add figures

@@

>>>>

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, 
                axis lines=left, xlabel={$s$}]
                \addplot[name path=f, dashed, black] {sqrt(x)};
                \addplot[name path=tildef, black, ultra thick] {sqrt(0.3+0.7*x)};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);

                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];

                \node[anchor=north west] at (axis cs: .05, .95) {Downstream};
                \node[anchor=south east] at (axis cs: .95, .05) {Upstream};
            \end{axis}
        \end{tikzpicture}
        \caption{Concave case}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick={0, 1}, yticklabels={0, f(1)},
                axis lines=left, xlabel={$s$}]
                \addplot[name path=f, dashed, black] {(x)^1.5};
                \addplot[name path=tildef, black, ultra thick] {(0.3+0.7*x)^1.5};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);

                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];

                \node[anchor=north west] at (axis cs: .05, .95) {Downstream};
                \node[anchor=south east] at (axis cs: .95, .05) {Upstream};
            \end{axis}
        \end{tikzpicture}
        \caption{Convex case}
    \end{subfigure}
    \caption{Illustration of \cref{prop:vertical_integration}}
    \label{fig:vertical_intergration}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.14, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick={0, 1, 1.14}, yticklabels={$0$, $f(1)$, $f(1 + \alpha)$},
                axis lines=left, xlabel={$s$}]
                \addplot[name path=f, dashed, black] {sqrt(x)};
                \addplot[name path=tildef, black, ultra thick] {sqrt(0.3+x)};
                \draw[dashed] (axis cs:0,1) -- (axis cs:1,1);
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1.14) -- (axis cs:1,1.14);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.14);

                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];

                \node[anchor=north west] at (axis cs: .05, 1.09) {Downstream};
                \node[anchor=south east] at (axis cs: .95, .05) {Upstream};
            \end{axis}
        \end{tikzpicture}
        \caption{Concave case}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.482, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick={0, 1, 1.482}, yticklabels={$0$, $f(1)$, $f(1 + \alpha)$},
                axis lines=left, xlabel={$s$}]
                \addplot[name path=f, dashed, black] {(x)^1.5};
                \addplot[name path=tildef, black, ultra thick] {(0.3+x)^1.5};
                \draw[dashed] (axis cs:0,1) -- (axis cs:1,1);
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1.482) -- (axis cs:1,1.482);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.482);

                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];

                \node[anchor=north west] at (axis cs: .05, 1.43) {Downstream};
                \node[anchor=south east] at (axis cs: .95, .05) {Upstream};
            \end{axis}
        \end{tikzpicture}
        \caption{Convex case}
    \end{subfigure}
    \caption{Illustration of \cref{prop:downstream_capacity}}
    \label{fig:upstream_capacity}
\end{figure}
